apply flashr2 with OCV

### 2018-01-10 analysis/templateforOCV.Rmd
Files commited by wflow_commit.

```{r}
PT_res = readRDS("../data/missingvalue/box_res_grids_sf_pmd/denoiseTumor_box.rds")
pt = plot_res(PT_res,"Tumor data")
pt
PT_res = readRDS("../data/missingvalue/box_res_grids_sf_pmd/TEXT_prsdt_box.rds")
pp = plot_res(PT_res,"Text data")
pp
```

>>>>

```{r}
PT_res = readRDS("../data/missingvalue/box_res_grids_sf_pmd/denoiseTumor_box.rds")
pt = plot_res(PT_res,"Tumor data")
pt
PT_res = readRDS("../data/missingvalue/box_res_grids_sf_pmd/TEXT_prsdt_box.rds")
pp = plot_res(PT_res,"Text data")
pp
PT_res = readRDS("../data/missingvalue/box_res_grids_sf_pmd/BreastCancer_box.rds")
pb = plot_res(PT_res,"Text data")
pb
```
